Title page

### 2025-09-16 output/Title_page.Rmd
Add Review 2 acknowledgements

The authors would like to thank Patricia Recio-Saboya, Ph.D.
(ORCID: [0000-0002-0530-4404](https://orcid.org/0000-0002-0530-4404))
for her valuable guidance regarding multidimensional estimation
in IRT software packages.

>>>>

The authors would like to thank:
[Patricia Recio-Saboya, Ph.D.](https://orcid.org/0000-0002-0530-4404),
for her valuable guidance regarding multidimensional estimation
in IRT software packages;
[Jay Verkuilen, Ph.D.,](https://orcid.org/0000-0003-3546-3411),
for his comments and suggestions regarding covariance whitening;
David Thissen and three additional anonymous reviewers for
their valuable comments and suggestions of early drafts of this manuscript.
